R Notebook

### 2017-07-12 doc/RMD/wmn-differentiation.Rmd
add DAPC for white mold nurseries

```{r AMOVA}
other(dat11cc)$REPLEN
bd <- bruvo.dist(dat11cc, replen = other(dat11cc)$REPLEN)
(ssc_amova <- poppr.amova(dat11cc, ~SourceType, dist = bd, quiet = TRUE))
ssc_amova_test <- randtest(ssc_amova, nrepet = 999)
plot(ssc_amova_test)
ssc_amova_test
```

@@

>>>>

```{r AMOVA, cache = TRUE}
other(dat11cc)$REPLEN
bd <- bruvo.dist(dat11cc, replen = other(dat11cc)$REPLEN)
(ssc_amova <- poppr.amova(dat11cc, ~SourceType, dist = bd, quiet = TRUE))
ssc_amova_test <- randtest(ssc_amova, nrepet = 999)
plot(ssc_amova_test)
ssc_amova_test
```

@@

## WMN DAPC

DAPC is a nice way of visualizing these. First, I'm simply going to compare 
between white mold nurseries and others:

```{r wmndapc, cache = TRUE}
filter <- strata(dat11cc) %>%
  group_by(Region) %>%
  mutate(filter = length(unique(SourceType)) > 1) %>%
  pull(filter)
wmn_compare <- dat11cc[filter]
set.seed(2017-07-12)
wmndapc <- xvalDapc(tab(wmn_compare), pop(wmn_compare), n.rep = 200, n.pca = 1:10)
wmndapc
scatter(wmndapc$DAPC)
(wmntab <- table(wmndapc$DAPC$assign, wmndapc$DAPC$grp))
chisq.test(wmntab, simulate.p.value = TRUE)
```

Okay, this shows that there's quite a bit of overlap between these two. What
happens if I look at the DAPC when it includes the pouplation groupings. Mainly,
I want to know if the white mold nurseries can be compared while considering the
pouplations

```{r wmndapcpop, fig.width = 8, fig.height = 10, cache = TRUE}
set.seed(2017-07-12)
wmndapc <- xvalDapc(tab(wmn_compare), strata(wmn_compare, ~SourceType/Region)[[2]], 
                    n.pca = 5:20, n.rep = 100)$DAPC
scatter(wmndapc)
LDS <- bind_cols(Population = wmndapc$grp, as.data.frame(wmndapc$ind.coord)) %>%
  as_tibble()
LDS_pop <- LDS %>% 
  group_by(Population) %>% 
  summarize_all(mean) %>%
  rename_all(function(x) gsub("LD", "mean", x))
LDS <- full_join(LDS, LDS_pop) %>%
  separate(Population, c("SourceType", "Pop"), remove = FALSE) 
LDS_PLOT <- ggplot(LDS, aes(x = LD1, y = LD2, color = SourceType)) + 
  geom_point(aes(fill = SourceType), alpha = 0.5, pch = 21, color = "black") +
  geom_segment(aes(x = mean1, y = mean2, xend = LD1, yend = LD2), alpha = 0.5) +
  stat_ellipse(type = "norm", level = 0.66, alpha = 0.75) + 
  # ggrepel::geom_label_repel(aes(x = mean1, y = mean2, label = Population), 
  #                           data = LDS_pop, show.legend = FALSE, color = "black") +
  theme_bw() +  
  theme(aspect.ratio = 1/1.618) +
  theme(legend.position = "bottom") +
  theme(axis.text = element_blank()) + 
  theme(axis.title = element_blank()) + 
  theme(axis.ticks = element_blank()) + 
  viridis::scale_color_viridis(discrete = TRUE, direction = -1) +
  viridis::scale_fill_viridis(discrete = TRUE, direction = -1) +
  scale_y_continuous(breaks = 0) + 
  scale_x_continuous(breaks = 0) + 
  theme(panel.background = element_rect(fill = "grey95")) +
  theme(panel.grid.major = element_line(color = "black"))

LDS_PLOT + facet_wrap(~Pop, ncol = 3)

```
